Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2016-12-02 longSC.tex
accepting ante's comment

However, difficulties in extracting $\eta/s$ in heavy-ion collisions can be attributed mostly to the fact that it strongly depends on the specific choice of the initial conditions~\cite{Romatschke:2007mq,Luzum:2012wu,Shen:2011zc}.
The viscous effects reduce the magnitude of the elliptic flow. Furthermore, the magnitude of $\eta/s$ used in hydrodynamic calculations should be considered as an average over the temperature evolution of the expanding fireball as it is known that $\eta/s$ of other fluids depends on temperature. 
In addition, part of the elliptic flow can also originate from the hadronic phase~\cite{Bozek:2011ua,Rose:2014fba,Ryu:2015vwa}. Therefore,
knowledge of both the temperature dependence of $\eta/s$ and the relative contributions from the partonic and hadronic phases should be understood better to quantify $\eta/s$ of the partonic fluid.

An important input to the hydrodynamic model simulations is the distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
This initial energy density profile can be quantified by calculating the distribution of the spatial eccentricity~\cite{Alver:2010gr},
\begin{equation}
 \varepsilon_{n} e^{in\Phi_{n}} = -\{r^n e^{in\phi}\}/ \{r^n\},
  \label{eq:eccentricities}
\end{equation}
where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Ref.~\cite{Teaney:2010vd,Niemi:2015qia}).
There are experimental and theoretical evidences~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g. $v_n \propto \varepsilon_n$ for n=2 or 3).
$v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower-order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
The higher harmonics ($n>3$) could be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics ~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}. When the order of harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and become larger for more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
The magnitude of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ is sensitive to ansatz used for the viscous distribution function, a correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
%and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
Hence the studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood part of hydrodynamic calculations~\cite{Teaney:2012ke,Niemi:2015qia}.

Recently, ALICE Collaboration measured for the first time the new multiparticle observables, the Symmetric 2-harmonic 4-particle Cumulants (SC), which quantify the relationship between event-by-event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}. 
The new observables are particularly robust against few-particle non-flow correlations and they provide independent information to recently analyzed symmetry plane correlators. 
It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of different order harmonic correlations would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
In this article, we have extended the analysis of SC observables to higher order Fourier harmonics (up to $5^{\mathrm{th}}$ order) as well as to $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).  We also include extensive comparison to hydrodynamic and AMPT model calculations.
In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods. The experimental setting and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}. Various theoretical models used in the article are described in Sec.~\ref{sec:models}. The results of the measurements are presented in Sec.~\ref{sec:results}.
 In Sec.~\ref{sec:theory} we present comparisons to theoretical calculations. Sec.~\ref{sec:summary} summarizes our findings.

@@

The systematic uncertainty due to the track reconstruction was estimated from comparison between results for the so-called standalone TPC tracks with the 
same parameters as described in Sec.~\ref{sec:experiment}, and combination of the TPC and the Inner Tracking System (ITS) detectors with tighter selection criteria.
To correct for non-uniform azimuthal acceptance due to dead zones in SPD, and to get the best transverse momentum resolution, approach of hybrid selection with SPD hit and/or ITS refit tracks combined with TPC were used. Then each track reconstruction was evaluated by varying the threshold on parameters used to select the tracks at the reconstruction level. 
The systematic difference of up to 12\% was observed in SC$(m,n)$ from the different track selections. 
In addition, we applied the like-sign technique to estimate non-flow contribution in SC$(m,n)$. The difference between two charged combinations and like-sign combinations were the largest contribution to the systematic uncertainty and they were about 7\% for SC(4,3) and 20\% for SC(5,3).

@@

\section{Summary}
\label{sec:summary}
In this article, we report the centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations.
The results are obtained by the Symmetric 2-harmonic 4-particle Cumulants (SC). It was demonstrated earlier in \cite{ALICE:2016kpq} that this method is insensitive to the non-flow effects and free from symmetry plane correlations.
We have found that fluctuations of $v_2$-$v_3$ and $v_3$-$v_4$ are anti-correlated in all centralities while fluctuations of $v_2$-$v_4$, $v_2$-$v_5$ and $v_3$-$v_5$ are correlated for all centralities. 
This measurement were compared to various hydrodynamic model calculations with different initial conditions as well as different parameterizations of the temperature dependence of $\eta/s$.
It is found that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties. Therefore they have discriminating power in separating the effects of $\eta/s$  from the initial conditions to the final state particle anisotropies.
The sign of $v_3$-$v_2$ correlation in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations.
In the most central collisions the anisotropies originate mainly from fluctuations, where the initial ellipsoidal geometry which is dominating in mid-central collisions plays little role. This observation might help to understand the details of the fluctuations in initial conditions. 
The comparisons to VISH2+1 calculation show that all the models with large $\eta/s$ regardless of the initial conditions failed to capture the centrality dependence of higher order correlations, more clearly than lower order harmonic correlations. 
Based on the tested model parameters, the $\eta/s$ should be small and AMPT initial condition is favored by the data. A quite clear separation of the correlation strength between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
Finally, we have found that $v_3$-$v_2$ and $v_4$-$v_2$ correlations have moderate $p_{\rm T}$ dependence in mid-central collisions. This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out.
The results presented in this article can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.

>>>>

Difficulties in extracting $\eta/s$ in heavy-ion collisions can be attributed mostly to the fact that it strongly depends on the specific choice of the initial conditions~\cite{Romatschke:2007mq,Luzum:2012wu,Shen:2011zc}.
The viscous effects reduce the magnitude of the elliptic flow. Furthermore, the magnitude of $\eta/s$ used in hydrodynamic calculations should be considered as an average over the temperature evolution of the expanding fireball as it is known that $\eta/s$ of other fluids depends on temperature. 
In addition, part of the elliptic flow can also originate from the hadronic phase~\cite{Bozek:2011ua,Rose:2014fba,Ryu:2015vwa}. Therefore,
knowledge of both the temperature dependence of $\eta/s$ and the relative contributions from the partonic and hadronic phases should be understood better to quantify $\eta/s$ of the partonic fluid.

An important input to the hydrodynamic model simulations is the distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
This initial energy density profile can be quantified by calculating the distribution of the spatial eccentricity~\cite{Alver:2010gr},
\begin{equation}
 \varepsilon_{n} e^{in\Phi_{n}} = -\{r^n e^{in\phi}\}/ \{r^n\},
  \label{eq:eccentricities}
\end{equation}
where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Ref.~\cite{Teaney:2010vd,Niemi:2015qia}).
There are experimental and theoretical evidences~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g. $v_n \propto \varepsilon_n$ for n=2 or 3).
$v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower-order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
The higher harmonics ($n>3$) could be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}. When the order of harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and become larger for more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
The magnitude of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ is sensitive to ansatz used for the viscous distribution function, a correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
%and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
Hence the studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood part of hydrodynamic calculations~\cite{Teaney:2012ke,Niemi:2015qia}.

Recently, ALICE Collaboration measured for the first time the new multiparticle observables, the Symmetric 2-harmonic 4-particle Cumulants (SC), which quantify the relationship between event-by-event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}. 
The new observables are particularly robust against few-particle non-flow correlations and they provide independent information to recently analyzed symmetry plane correlators. 
It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of different order harmonic correlations would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
In this article, we have extended the analysis of SC observables to higher order Fourier harmonics (up to $5^{\mathrm{th}}$ order) as well as to $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).  We also include extensive comparison to hydrodynamic and AMPT model calculations.
In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods. The experimental setting and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}. The results of the measurements are presented in Sec.~\ref{sec:results}. 
 In Sec.~\ref{sec:theory} we present comparisons to theoretical calculations. Various theoretical models used in the article are described in Sec.~\ref{sec:models}. Sec.~\ref{sec:summary} summarizes our findings.

@@

The systematic uncertainty due to the track reconstruction was estimated from comparison between results for the so-called standalone TPC tracks with the 
same parameters as described in Sec.~\ref{sec:experiment}, and combination of the TPC and the Inner Tracking System (ITS) detectors with tighter selection criteria.
To correct for non-uniform azimuthal acceptance due to dead zones in SPD, and to get the best transverse momentum resolution, approach of hybrid selection with SPD hit and/or ITS refit tracks combined with TPC were used. Then each track reconstruction was evaluated by varying the threshold on parameters used to select the tracks at the reconstruction level. 
The systematic difference of up to 12\% was observed in SC$(m,n)$ from the different track selections. 
In addition, we applied the like-sign technique to estimate non-flow contribution in SC$(m,n)$. The difference between results obtained by selecting all charged particles and results obtained after either selecting only positively or only negatively charged particles was the largest contribution to the systematic uncertainty and it is about 7\% for SC(4,3) and 20\% for SC(5,3).

@@

\section{Summary}
\label{sec:summary}
In this article, we report the centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations.
The results are obtained by the Symmetric 2-harmonic 4-particle Cumulants (SC). It was demonstrated earlier in \cite{ALICE:2016kpq} that this method is insensitive to the non-flow effects and free from symmetry plane correlations.
We have found that fluctuations of $v_2$-$v_3$ and $v_3$-$v_4$ are anti-correlated in all centralities while fluctuations of $v_2$-$v_4$, $v_2$-$v_5$ and $v_3$-$v_5$ are correlated for all centralities. 
This measurement were compared to various hydrodynamic model calculations with different initial conditions as well as different parameterizations of the temperature dependence of $\eta/s$.
It is found that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties. Therefore they have discriminating power in separating the effects of $\eta/s$  from the initial conditions to the final state particle anisotropies.
The sign of $v_3$-$v_2$ correlation in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations.
In the most central collisions the anisotropies originate mainly from fluctuations, where the initial ellipsoidal geometry which is dominating in mid-central collisions plays little role. This observation might help to understand the details of the fluctuations in initial conditions. 
The comparisons to VISH2+1 calculation show that all the models with large $\eta/s$ regardless of the initial conditions failed to capture the centrality dependence of higher order correlations, more clearly than lower order harmonic correlations. 
Based on the tested model parameters, the $\eta/s$ should be small and AMPT initial condition is favored by the data. A quite clear separation of the correlation strength between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
The default configuration of AMPT model describes well the normalized symmetric cumulants (NSC($m$,$n$)) for most of centralities and for most combinations of harmonics which were considered. Together with the measurements of individual harmonics these results provide further constraints on the system properties and help discriminating between theoretical models.
Finally, we have found that $v_3$ and $v_2$, $v_4$ and $v_2$ correlations have moderate $p_{\rm T}$ dependence in mid-central collisions. This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out.
The results presented in this article can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
